Process Genotypes For Ancestry Analysis

### 2019-09-18 code/Ancestry_PCA.Rmd
Finished Diagnosis Regression

wget ftp://ftp.1000genomes.ebi.ac.uk/vol1/ftp/phase1/analysis_results/integrated_call_sets/integrated_call_samples.20101123.ALL.panel

@@

tar -xvf phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz.tgz

for i in {1..22}
do
    tabix -p vcf chr$i\.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz
done

>>>>

#ID Sample list of needed Ref Populations
wget ftp://ftp.1000genomes.ebi.ac.uk/vol1/ftp/phase1/analysis_results/integrated_call_sets/integrated_call_samples.20101123.ALL.panel

@@

for i in {1..22}
do
    wget ftp://ftp.1000genomes.ebi.ac.uk/vol1/ftp/phase1/analysis_results/integrated_call_sets/ALL.chr1.integrated_phase$i\_v3.20101123.snps_indels_svs.genotypes.vcf.gz
     wget ftp://ftp.1000genomes.ebi.ac.uk/vol1/ftp/phase1/analysis_results/integrated_call_sets/ALL.chr1.integrated_phase$i\_v3.20101123.snps_indels_svs.genotypes.vcf.gz.tbi
    #tabix -p vcf chr$i\.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz
done

#tar -xvf phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz.tgz
